---
title: "Dplyr homework"
author: "Leopold Gross"
format: html
editor: visual
echo: false 
message: false
---

```{r}
#| echo: false
#| message: false
here::i_am("dplyr.Rproj")

library(here)
library(dplyr)
```

```{r}
spotify <- readRDS('top-spotify-hits.Rds')

```

## EX1

Question 1

the data set contains `r count(spotify%>%distinct(song))` songs, `r count(spotify%>%distinct(artist))` artists and `r count(spotify%>%distinct(genre))` genres.

Question 2

```{r}
spotify %>% group_by(year) %>% dplyr::summarise(song = n()) %>% knitr::kable()
  
```

Question 3

The most popular artist is `r spotify %>% distinct(song, artist) %>% count(artist) %>% slice_max(n)` songs of her are in the spotify top songs !

Question 4

```{r}
spotify %>% group_by(genre) %>% summarise(avg_bpm=mean(tempo), med_bpm=median(tempo), max(tempo), min(tempo)) %>% knitr::kable()
```

Question 5

```{r}
spotify %>% group_by(year) %>% summarise(med_nrgy=median(energy), med_danceability=median(danceability)) %>% knitr::kable()
```

Question 6

```{r}
library(ggplot2)

median_values <-spotify %>% group_by(year) %>% summarise(med_nrgy=median(energy), med_danceability=median(danceability)) 

ggplot(median_values, aes(x = year)) +
  geom_line(aes(y = med_nrgy, color = "Median Energy")) +
  geom_line(aes(y = med_danceability, color = "Median Danceability")) 
```

## EXERCISE 2

Question 1

```{r}

#| echo: false
#| message: false
dropout <- readRDS('dropout.RDS')

dropout %>%  group_by(Gender, `Marital status`) %>% summarise(median_age=median(`Age at enrollment`)) %>%  knitr::kable()



```

question 2

```{r}
library(tidyr)
#| echo: false
#| message: false

dropout %>% 
  group_by(Gender, `Marital status`) %>% summarise(median_age=median(`Age at enrollment`)) %>% pivot_wider(names_from = Gender, values_from = `Marital status`) %>% knitr::kable()
```

question 3

```{r}
dataframe <- dropout %>% group_by(Target) %>% summarise_at(vars(starts_with("Curricular units")), mean) %>% knitr::kable()
dataframe
```

Question 4

```{r}
dropout %>% group_by(Target) %>% summarise_at(vars(starts_with("Curricular units")), mean) %>% pivot_longer(starts_with("Curricular units"), names_to = "Units") %>% pivot_wider(names_from = Target) %>% knitr::kable()
```

